Reproducibility in plant pathology: where do we stand and a way forward

### 2022-04-08 analysis/paper/paper.Rmd
Update authors' contributions
clean up parens around package versions

Model finesses were evaluated using model summaries and diagnostic plots from 'brms' 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' ((version `r packageVersion("bayesplot")`)) [@Gabry2019].

@@

A.H.S, E.DP., Z.F. and N.J.G. conceived of the presented idea and scoring system.
N.J.G. provided five-year impact factors.
A.H.S., E.DP., Z.F. and K.dSA. evaluated articles for scoring.
A.H.S. designed the computational framework for analysis and created the research compendium with feedback from E.DP. and Z.F.
A.H.S. wrote the manuscript in consultation with E.DP.
All authors provided critical feedback and helped contribute to the final version of the manuscript.

>>>>

Model finesses were evaluated using model summaries and diagnostic plots from 'brms' 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].

@@

A.H.S, E.DP., Z.F. and N.J.G. conceived of the presented idea and scoring system.
E.DP. provided five-year impact factors.
A.H.S., E.DP., Z.F. K.A. and N.G. evaluated articles for scoring.
A.H.S. designed the computational framework for analysis and created the research compendium with feedback from E.DP. and Z.F.
A.H.S. wrote the manuscript in consultation with E.DP.
All authors provided critical feedback and helped contribute to the final version of the manuscript.
